### 2016-03-23 paper.tex
Add three images and mention design logs

\documentclass[a4paper]{article}                                     
\usepackage{url,xspace,epsfig,etoolbox}
\usepackage{natbib}
\usepackage{fullpage}
\usepackage[font=bf]{caption}
\usepackage{mdwlist}

@@

Our experiment involved a team of eleven undergraduate students and a
faculty mentor.  The students majors include Computer Science, English
(Creative Writing), Philosophy, Telecommunications (Audio Production),
and Art (Animation).
Each student earned three credit hours for the experience during a fifteen-week
semester,
working together in a studio space for two hours each Monday, Wednesday,
and Friday.
% In future version, cite the TOCE paper
The team collectively agreed upon three primary goals for the design
experiment in the cultural-narration genre:
to use narrative as the primary form of player feedback;
to teach cultural empathy;
and to use technology to address complications of analog implementations.

Given these goals, the team proceeded with an incremental and
iterative approach to game design and development, each iteration
producing an executable release in accordance with best practices of
agile software development~\citep[see, for
example,][]{Cockburn2006,Keith2010}.  Each iteration was tested at
\textit{[the library branch]}, providing valuable feedback to the
team.  Each iteration concluded with a retrospective
meeting~\citep{Kerth2001}, which provided an opportunity for the
team's reflective practice~\citep{Schon1984}.
The results of these retrospectives included large and small changes
to the team's methodology, including a transition from
story mapping~\citep{Patton2014} to Scrum~\citep{Schwaber2013}.
In addition to paper prototypes, the team 
developed prototypes using JavaFX, PlayN, and Polymer, 
all of which allow for HTML5 Web deployment.
Game images and stories were inspired by the team's research on monsters
from world cultures, which included both research sources
(such as \citet{Cohen1996}) and children's books (especially
\citet{Steer2008} and \citet{Stowell2013}).
The team also consulted with local university experts on
games, monsters, world cultures, and literacy.

>>>>

\documentclass[a4paper]{article}                                     
\usepackage{url,xspace,epsfig,etoolbox}
\usepackage{natbib}
\usepackage{fullpage}
\usepackage[font=bf]{caption}
\usepackage{mdwlist}
\usepackage{graphicx}

@@

A team of eleven undergraduate students, working with a faculty mentor,
undertook a design experiment and pilot study to explore a monster-themed
culture-narration game.
The students' majors include Computer Science, English
(Creative Writing), Philosophy, Telecommunications (Audio Production),
and Art (Animation).
Each student earned three credit hours for the experience during a fifteen-week
semester,
working together in a studio space for two hours each Monday, Wednesday,
and Friday.
% In future version, cite the TOCE paper
The team collectively agreed upon three primary goals for the design
experiment in the cultural-narration genre:
to use narrative as the primary form of player feedback;
to teach cultural empathy;
and to use technology to address complications of analog implementations.

Given these goals, the team proceeded with an incremental and
iterative approach to game design and development.
The team used a design log to record design decisions~\citep{Cook2011},
and each iteration
produced an executable release in accordance with best practices of
agile software development~\citep[see, for example,][]{Cockburn2006,Keith2010}. 
Figures~\ref{fig:screenshots} and~\ref{fig:paper-prototype} demonstrate
design artifacts from the design and development process.
Each iteration was tested at
\textit{[the library branch]}, providing valuable feedback to the
team.  Each iteration concluded with a retrospective
meeting~\citep{Kerth2001}, which provided an opportunity for the
team's reflective practice~\citep{Schon1984}.
The results of these retrospectives included large and small changes
to the team's methodology, including a transition from
story mapping~\citep{Patton2014} to Scrum~\citep{Schwaber2013}.
In addition to paper prototypes, the team 
developed prototypes using JavaFX, PlayN, and Polymer, 
all of which allow for HTML5 Web deployment.
Game images and stories were inspired by the team's research on monsters
from world cultures, which included both research sources
(such as \citet{Cohen1996}) and children's books (especially
\citet{Steer2008} and \citet{Stowell2013}).
The team also consulted with local university experts on
games, monsters, world cultures, and literacy.

\newcommand{\figwidth}{2.5in}
\begin{figure}
\centering
\includegraphics[width=\figwidth]{iteration-1}
\includegraphics[width=\figwidth]{kappa-encounter}
\caption{Screenshots from Iteration 1 (left) and 2 (right)}
\label{fig:screenshots}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\figwidth]{paper-prototype}
\caption{Paper prototype from Iteration 3}
\label{fig:paper-prototype}
\end{figure}
